Study of the hadronization of charged pions

### 2016-09-21 AnalysisNote.tex
Author update

\title{Study of the hadronization of $\pi^-$}

\author{Rapha\"el \textsc{Dupr\'e}, 
Lamiaa \textsc{El Fassi}\thanks{also {\it Rutgers University}} , 
Kawtar \textsc{Hafidi} ... \\ 
{\it Physics Division, Argonne National Laboratory,} \\
{\it Argonne, Illinois 60439, USA} }

>>>>

\title{Study of the hadronization of charged pions}

\author{
  Rapha\"el \textsc{Dupr\'e} \\ 
  {\it Institut de Physique Nucl\'eaire, Orsay, France} \\
  Lamiaa \textsc{El Fassi} \\ 
  {\it Mississippi State University, Mississippi State,} \\ 
  {\it Mississippi 39762, USA} \\
  Kawtar \textsc{Hafidi} \\ 
  {\it Physics Division, Argonne National Laboratory,} \\ 
  {\it Argonne, Illinois 60439, USA} 
}
